Are translation equivalents special? Evidence from simulations and empirical data from bilingual infants

### 2021-06-16 paper/paper_TE_bilingual_vocabulary_model_docx.Rmd
fixed typos/wordings

author: 
  - name          : "Rachel Ka-Ying Tsui"
    affiliation   : "1, 2"
    corresponding : yes    
    address       : "Department of Psychology, 7141 Sherbrooke St. West, Montreal, QC, Canada, H2T1V2, or Laboratory for Language Development, RIKEN Center for Brain Science, 2-1 Hirosawa, Wako-shi, Saitama, Japan, 351-0198"
    email         : "rachelkytsui@gmail.com"
  - name          : "Ana Maria Gonzalez-Barrero"
    affiliation   : "1" 
  - name          : "Esther Schott"
    affiliation   : "1" 
  - name          : "Krista Byers-Heinlein"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Concordia University"
  - id            : "2"
    institution   : "Laboratory for Language Development, RIKEN Center for Brain Science"

@@

class             : "man"
output            : papaja::apa6_pdf # change to apa6_docx for word document
citation_package  : biblatex
nocite: '@*' # include all the references in the .bib file, because in-text citations were mostly typed manually to fit the apa7 style
---

@@

```{r load_packages_settings, include = FALSE}
library(rmarkdown)
library(knitr)
library(papaja)
library(kableExtra)
library(english)
library(here)
library(tidyverse)
library(tidylog)
library(wordbankr)
library(ggplot2)
library(patchwork)
library(gridExtra)
library("ggpubr")
library(broom)
library(lsr)
library(Hmisc)
library(lme4)
library(lmerTest)
library(scales)

@@

kable(box1,
      format="latex", booktabs=TRUE, longtable = TRUE) %>%
  column_spec(1, width = "450px") %>%
  kable_styling(font_size = 9)

@@

landscape(
  kable(table1,
        format = "latex", booktabs = TRUE,
        caption = "Table 1. Summary of the parameters in the Bilingual Vocabulary Model.") %>%
    kableExtra::kable_styling(font_size = 7) %>%
    pack_rows("Main Parameters", 1, 4) %>%
    pack_rows("Derived Parameters", 5, 10) %>%
    column_spec(2:4, width = "175px") %>%
    footnote(general = "All vocabulary measures are constrained to be integers.")
)
```

@@

# print table
#papaja::apa_table(mean_TE_binBALANCE,
#                  caption = "Average number of translation equivalents (TE) produced by each balance group.",
#                  col.names =c("","N","Mean","$SD$","range"),
#                  align="c")

kable(mean_TE_binBALANCE,
      format="latex", booktabs=TRUE, align = "c",
      caption = "Table 6. Average number of translation equivalents (TE) produced by each balance group.") %>%
  column_spec(1, width = "150px") %>%
  column_spec(2:4, width = "50px") %>%
  column_spec(5, width = "75px") %>%
  kable_styling(position = "center")
```

>>>>

author: 
  - name          : "Rachel Ka-Ying Tsui"
    affiliation   : "1, 2"
    corresponding : yes    
    address       : "Department of Psychology, 7141 Sherbrooke St. West, Montreal, QC, Canada, H2T1V2.  Current address: Laboratory for Language Development, RIKEN Center for Brain Science, 2-1 Hirosawa, Wako-shi, Saitama, Japan, 351-0198"
    email         : "rachelkytsui@gmail.com"
  - name          : "Ana Maria Gonzalez-Barrero"
    affiliation   : "1" 
  - name          : "Esther Schott"
    affiliation   : "1" 
  - name          : "Krista Byers-Heinlein"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Concordia University"

@@

class             : "man"
output            : papaja::apa6_docx # change to apa6_docx for word document
citation_package  : biblatex
nocite: '@*' # include all the references in the .bib file, because in-text citations were mostly typed manually to fit the apa7 style
---

@@

```{r load_packages_settings, include = FALSE}
library(rmarkdown)
library(knitr)
library(papaja)
library(kableExtra)
library(flextable)
library(english)
library(here)
library(tidyverse)
library(tidylog)
library(wordbankr)
library(ggplot2)
library(patchwork)
library(gridExtra)
library("ggpubr")
library(broom)
library(lsr)
library(Hmisc)
library(lme4)
library(lmerTest)
library(scales)

@@

#kable(box1,
#      format="latex", booktabs=TRUE, longtable = TRUE) %>%
#  column_spec(1, width = "450px") %>%
#  kable_styling(font_size = 9)

flextable(box1) %>%
  width(width = 6.5)

@@

#landscape(
#  kable(table1,
#        format = "latex", booktabs = TRUE,
#        caption = "Table 1. Summary of the parameters in the Bilingual Vocabulary Model.") %>%
#    kableExtra::kable_styling(font_size = 7) %>%
#    pack_rows("Main Parameters", 1, 4) %>%
#    pack_rows("Derived Parameters", 5, 10) %>%
#    column_spec(2:4, width = "175px") %>%
#    footnote(general = "All vocabulary measures are constrained to be integers.")
#)

flextable(table1) %>%
  fontsize(part = "all", size = 8) %>% 
  set_header_labels(Relationship.to.other.parameters = "Relationship to other parameters") %>%
  set_caption("Table 1. Summary of the parameters in the Bilingual Vocabulary Model.") %>%
  width(width = 2)

@@

# print table
papaja::apa_table(mean_TE_binBALANCE,
                  caption = "Average number of translation equivalents (TE) produced by each balance group.",
                  col.names =c("","N","Mean","$SD$","range"),
                  align="c")

#kable(mean_TE_binBALANCE,
#      format="latex", booktabs=TRUE, align = "c",
#      caption = "Table 6. Average number of translation equivalents (TE) produced by each balance group.") %>%
#  column_spec(1, width = "150px") %>%
#  column_spec(2:4, width = "50px") %>%
#  column_spec(5, width = "75px") %>%
#  kable_styling(position = "center")
```
